Advancements in Moltres for Time-Dependent Multiphysics Molten Salt Reactor Modeling

### 2024-12-12 presentation/1d.tex
slide edits

  All 1-D cases ran on each of the following numerical solvers:
  \begin{enumerate}
    \item OpenMC in continuous energy mode (OpenMC-CE)
    \item OpenMC in multigroup mode (OpenMC-MG)
    \item Standard neutron diffusion method (Moltres \& Python)
    \item $S_8$ method (Moltres \& Python)
    \item Hybrid $S_8$-diffusion method (Moltres \& Python)
  \end{enumerate}
  \vspace{.2cm}

@@

\begin{frame}
%  \frametitle{Hybrid $S_N$-Diffusion Method: 1-D Neutronics Eigenvalue Simulations}
  \begin{columns}
    \column{5.5cm}
    \textbf{Case 3b Neutron Flux Distributions}
    \begin{itemize}
      \item The neutron diffusion and hybrid methods fare worse than the $S_8$ method at capturing
        the oscillatory flux pattern.
      \item The hybrid method performs better than the neutron diffusion method near $x=0$ cm where
        the control rod is situated.
    \end{itemize}
    \column{5.5cm}
    \begin{figure}[htb!]
      \centering
      \includegraphics[width=.975\columnwidth]{case-3b-flux-diff}
      \caption{Absolute difference in neutron group flux distributions for Case 3b from Moltres-$S_8$,
      Moltres-diffusion, Moltres-hybrid, and Python-hybrid relative to OpenMC-MG.}
      \label{fig:3b-flux-diff}
    \end{figure}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{1-D MSRE Neutronics Simulation Results}
  \textbf{Impact of Correction Subregion Sizes on Rod Worth}
  \begin{itemize}
    \item Rod worth estimates vary non-monotonically with increasing correction subregion size.
    \item Rod worth estimates remain within 0.2 \% of the $S_8$ method rod worth.
    \item The hybrid method produces accurate rod worth estimates as long as the correction region
      size is kept consistent.
  \end{itemize}
  \begin{figure}[htb!]
    \centering
    \includegraphics[width=0.6\columnwidth]{correction-size-rho}
    \caption{Percentage difference in rod worth from the hybrid method relative to OpenMC-CE for
      Cases 3a and 3b with different correction subregion sizes. The horizontal lines indicate
      equivalent rod worth differences from the OpenMC-MG and $S_8$ methods.}
    \label{fig:v1-size-rho}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{1-D MSRE Neutronics Simulation Results}
  \begin{columns}
    \column{7cm}
    \textbf{Relaxing the $S_N$ Convergence Tolerance}
    \begin{itemize}
      \item Transport correction parameters converge faster than scalar flux in the $S_N$ subsolver.
      \item Relaxing the $S_N$ subsolver convergence tolerance would provide computational savings.
      \item The hybrid method exhibits superlinear ($q=1.333$) convergence in $k$ with respect to
        the $S_8$ convergence tolerance value.
    \end{itemize}
    \begin{table}[h]
      \centering
      \caption{Number of outer iterations in hybrid method calculations of Case 3b for a given set of
      convergence tolerance values imposed on the $S_8$ subsolver.}
      \small
      \setlength\tabcolsep{2pt}
      \begin{tabular}{l S S S S S S}
        \toprule
        $S_8$ subsolver tolerance, $\epsilon_\text{tol}$ & {$10^{-8}$} & {$10^{-7}$} & {$10^{-6}$} & {$10^{-5}$} & {$10^{-4}$} & {$10^{-3}$} \\
        \midrule
        Number of outer iterations & 3 & 3 & 3 & 2 & 2 & 1 \\
        \bottomrule
      \end{tabular}
      \label{table:sn-tol}
    \end{table}
    \column{4cm}
    \begin{figure}[h]
      \centering
      \includegraphics[width=\columnwidth]{sn-tol}
      \caption{$k_\text{eff}$ error estimates of Case 3b for a range of convergence tolerance values
      imposed on the $S_8$ subsolver relative to the reference $k_\text{eff}$ value when
      $\epsilon_\text{tol}=10^{-8}$.}
      \label{fig:sn-tol}
    \end{figure}
  \end{columns}
\end{frame}

>>>>

  All 1-D cases ran on each of the following numerical solvers:
  \begin{enumerate}
    \item OpenMC in continuous energy mode (OpenMC-CE)
    \item OpenMC in multigroup mode (OpenMC-MG)
    \item Neutron diffusion method (Moltres \& Python)
    \item $S_8$ method (Moltres \& Python)
    \item Hybrid $S_8$-diffusion method (Moltres \& Python)
  \end{enumerate}
  \vspace{.2cm}

@@

\begin{frame}
  \frametitle{1-D MSRE Neutronics Simulation Results}
  \textbf{Case 3b Geometry}
  \begin{figure}
    \centering
    \includegraphics[width=.7\textwidth]{hybrid-illustration}
    \caption{Geometry of 1-D Case 3b.}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{1-D MSRE Neutronics Simulation Results}
  \textbf{Case 3b Neutron Flux Distributions}
  \begin{figure}[htb!]
    \centering
    \includegraphics[width=.75\columnwidth]{images/case-3b-flux-diff-pres}
    \caption{Absolute difference in neutron group flux distributions for Case 3b from Moltres-$S_8$,
    Moltres-diffusion, and Moltres-hybrid relative to OpenMC-MG.}
    \label{fig:3b-flux-diff}
  \end{figure}
%  \begin{itemize}
%    \item The neutron diffusion and hybrid methods fare worse than the $S_8$ method at capturing
%      the oscillatory flux pattern.
    The hybrid method provides more accurate flux estimates than the neutron diffusion method near $x=0$ cm where
      the control rod is situated.
%  \end{itemize}
\end{frame}

%\begin{frame}
%%  \frametitle{Hybrid $S_N$-Diffusion Method: 1-D Neutronics Eigenvalue Simulations}
%  \begin{columns}
%    \column{5.5cm}
%    \textbf{Case 3b Neutron Flux Distributions}
%    \begin{itemize}
%      \item The neutron diffusion and hybrid methods fare worse than the $S_8$ method at capturing
%        the oscillatory flux pattern.
%      \item The hybrid method performs better than the neutron diffusion method near $x=0$ cm where
%        the control rod is situated.
%    \end{itemize}
%    \column{5.5cm}
%    \begin{figure}[htb!]
%      \centering
%      \includegraphics[width=.975\columnwidth]{case-3b-flux-diff}
%      \caption{Absolute difference in neutron group flux distributions for Case 3b from Moltres-$S_8$,
%      Moltres-diffusion, Moltres-hybrid, and Python-hybrid relative to OpenMC-MG.}
%      \label{fig:3b-flux-diff}
%    \end{figure}
%  \end{columns}
%\end{frame}

\begin{frame}
  \frametitle{1-D MSRE Neutronics Simulation Results}
  \textbf{Impact of Correction Subregion Sizes on Rod Worth}
  \begin{itemize}
    \item Rod worth estimates vary non-monotonically with increasing correction subregion size.
    \item Rod worth estimates remain within 0.2\% of the $S_8$ method rod worth.
    \item The hybrid method produces accurate rod worth estimates as long as the correction region
      size is kept consistent.
  \end{itemize}
  \begin{figure}[htb!]
    \centering
    \includegraphics[width=0.6\columnwidth]{correction-size-rho}
    \caption{Percentage difference in rod worth from the hybrid method relative to OpenMC-CE for
      Cases 3a and 3b with different correction subregion sizes.}
    \label{fig:v1-size-rho}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{1-D MSRE Neutronics Simulation Results}
  \begin{columns}
    \column{6.5cm}
    \textbf{Relaxing the $S_N$ Convergence Tolerance,} $\bm{\epsilon}_\text{tol}$
    \begin{itemize}
      \item Transport correction parameters converge faster than scalar flux in the $S_N$ subsolver.
      \item Relaxing the $S_N$ subsolver convergence tolerance would provide computational savings.
      \item The hybrid method exhibits superlinear ($q=1.333$) convergence in $k$ with respect to
        the $S_8$ convergence tolerance value.
    \end{itemize}
    \begin{table}[h]
      \centering
      \caption{Number of outer iterations in hybrid method calculations of Case 3b for a given set of
      convergence tolerance values imposed on the $S_8$ subsolver.}
      \small
      \setlength\tabcolsep{2pt}
      \begin{tabular}{l S S S S S S}
        \toprule
        Tolerance value, $\epsilon_\text{tol}$ & {$10^{-8}$} & {$10^{-7}$} & {$10^{-6}$} & {$10^{-5}$} & {$10^{-4}$} & {$10^{-3}$} \\
        \midrule
        No.\ of outer iterations & 3 & 3 & 3 & 2 & 2 & 1 \\
        \bottomrule
      \end{tabular}
      \label{table:sn-tol}
    \end{table}
    \column{4.5cm}
    \begin{figure}[h]
      \centering
      \includegraphics[width=\columnwidth]{sn-tol}
      \caption{$k_\text{eff}$ error estimates of Case 3b for a range of $S_8$ subsolver convergence tolerance values
      relative to the reference $k_\text{eff}$ value when
      $\epsilon_\text{tol}=10^{-8}$.}
      \label{fig:sn-tol}
    \end{figure}
  \end{columns}
\end{frame}

### 2024-12-12 presentation/2d.tex
slide edits

\begin{frame}
  \frametitle{2-D MSRE Neutronics Simulation Results}
  \textbf{2-D Quarter-Core $k$ \& Rod Worth Results}
  \begin{table}[htb]
    \small
    \centering
    \caption{$k_\text{eff}$ and control rod worth estimates for the 2-D quarter-core \gls{MSRE}
      model. Error values are relative to OpenMC-CE.}
    \setlength\tabcolsep{2pt}
    \begin{tabular}{l S[table-format=1.5(2)] S S[table-format=1.5(2)] S S[table-format=4(2)] S}
      \toprule
      \multirow{2}{*}{Method} & \multicolumn{2}{c}{No Rod} & \multicolumn{2}{c}{Rod} & \multicolumn{2}{c}{Rod worth} \\
                              & {$k_\text{eff}$} & {Error [pcm]} & {$k_\text{eff}$} & {Error [pcm]} & {$\Delta\rho_\text{worth}$ [pcm]} & {Error [pcm]} \\
                              \cmidrule(r){1-1} \cmidrule(rl){2-3} \cmidrule(rl){4-5} \cmidrule(l){6-7}
  	  OpenMC-CE & 1.11209(43) & {-} & 1.01740(42) & {-} & 8370(53) & {-} \\
  	  OpenMC-MG & 1.11979(42) & 618 & 1.02204(41) & 446 & 8541(51) & 172 \\
        Diffusion & 1.12059 & 682 & 1.00903 & -816 & 9867 & 1484 \\
        Hybrid & 1.12174 & 773 & 1.02532 & 760 & 8383 & 13 \\
      \bottomrule
    \end{tabular}
    \label{table:quarter-core}
  \end{table}
  \vspace{.2cm}

@@

\begin{frame}
  \frametitle{2-D MSRE Neutronics Simulation Results}
  \textbf{2-D Quarter-Core Normalized Fuel Channel Power Distribution}
  \begin{table}[htb]
    \small
    \centering
    \caption{Absolute mean and maximum percentage errors in the normalized channel fission rates of
    the 2-D \gls{MSRE} quarter-core models relative to OpenMC. The mean relative standard deviation of
    OpenMC normalized channel fission rates is 0.20\%.}
    \begin{tabular}{l S S S S}
      \toprule
      \multirow{2}{*}{Method} & \multicolumn{2}{c}{No Rod} & \multicolumn{2}{c}{Rod} \\
                              & {Mean [\%]} & {Maximum [\%]} & {Mean [\%]} & {Maximum [\%]} \\
                              \cmidrule(r){1-1} \cmidrule(rl){2-3} \cmidrule(l){4-5}
      Diffusion & 0.40 & 2.63 & 2.01 & 17.44 \\
      Hybrid & 0.40 & 1.32 & 0.43 & 3.08 \\
      \bottomrule
    \end{tabular}
    \label{table:quarter-core-power}
  \end{table}
  \vspace{.2cm}

@@

\begin{frame}
  \frametitle{2-D MSRE Neutronics Simulation Results}
  \textbf{2-D Full-Core Normalized Fuel Channel Power Distribution}
  \begin{table}[htb]
    \footnotesize
    \centering
    \caption{Absolute mean and maximum percentage errors in the normalized channel fission rates of
    the 2-D \gls{MSRE} full-core models relative to OpenMC. The mean relative standard deviation of
    OpenMC normalized channel fission rates is 0.27\%.}
    \setlength\tabcolsep{1pt}
    \begin{tabular}{l S S S S S S S S}
      \toprule
      \multirow{2}{*}{Method} & \multicolumn{2}{c}{No Rod} & \multicolumn{2}{c}{Rod 1} & \multicolumn{2}{c}{Rod 1 \& 2} & \multicolumn{2}{c}{Rod 1, 2 \& 3} \\
                              & {Mean [\%]} & {Maximum [\%]} & {Mean [\%]} & {Maximum [\%]} & {Mean [\%]} & {Maximum [\%]} & {Mean [\%]} & {Maximum [\%]} \\
                              \cmidrule(r){1-1} \cmidrule(rl){2-3} \cmidrule(rl){4-5} \cmidrule(rl){6-7} \cmidrule(l){8-9}
      Diffusion & 0.45 & 2.95 & 0.94 & 12.61 & 1.35 & 15.34 & 1.67 & 17.09 \\
      Hybrid & 0.43 & 1.45 & 0.43 & 1.82 & 0.43 & 2.26 & 0.43 & 2.52 \\
      \bottomrule
    \end{tabular}
    \label{table:full-core-power}
  \end{table}
  \vspace{.2cm}

  \begin{itemize}
    \item Mean percentage error for the hybrid method remains consistent at 0.43 \%.
    \item Significant improvement in maximum percentage error of the channel fission rate.
  \end{itemize}
\end{frame}

>>>>

\begin{frame}
  \frametitle{2-D MSRE Neutronics Simulation Results}
  \textbf{2-D Quarter-Core $\bm{k}$ \& Rod Worth Results}
  \begin{table}[htb]
    \small
    \centering
    \caption{$k_\text{eff}$ and control rod worth estimates for the 2-D quarter-core \gls{MSRE}
      model. Error values are relative to OpenMC-CE.}
    \setlength\tabcolsep{2pt}
    \begin{tabular}{l S[table-format=1.5(2)] S S[table-format=1.5(2)] S S[table-format=4(2)] S}
      \toprule
      \multirow{2}{*}{Method} & \multicolumn{2}{c}{No Rod} & \multicolumn{2}{c}{Rod} & \multicolumn{2}{c}{Rod worth} \\
                              & {$k_\text{eff}$} & {Error [pcm]} & {$k_\text{eff}$} & {Error [pcm]} & {$\Delta\rho_\text{worth}$ [pcm]} & {Error [pcm]} \\
                              \cmidrule(r){1-1} \cmidrule(rl){2-3} \cmidrule(rl){4-5} \cmidrule(l){6-7}
  	  OpenMC-CE & 1.11209(43) & {-} & 1.01740(42) & {-} & 8370(53) & {-} \\
  	  OpenMC-MG & 1.11979(42) & 618 & 1.02204(41) & 446 & 8541(51) & 172 \\
        Diffusion & 1.12059 & 682 & 1.00903 & -816 & 9867 & 1484 \\
        Hybrid & 1.12174 & 773 & 1.02532 & 760 & 8383 & 13 \\
      \bottomrule
    \end{tabular}
    \label{table:quarter-core}
  \end{table}
  \vspace{.2cm}

@@

\begin{frame}
  \frametitle{2-D MSRE Neutronics Simulation Results}
  \textbf{2-D Quarter-Core Normalized Channel Fission Rate Distribution}
  \begin{table}[htb]
    \small
    \centering
    \caption{Absolute mean and maximum percentage errors in the normalized channel fission rates of
    the 2-D \gls{MSRE} quarter-core models relative to OpenMC. The mean relative standard deviation of
    OpenMC normalized channel fission rates is 0.20\%.}
    \begin{tabular}{l S S S S}
      \toprule
      \multirow{2}{*}{Method} & \multicolumn{2}{c}{No Rod} & \multicolumn{2}{c}{Rod} \\
                              & {Mean [\%]} & {Maximum [\%]} & {Mean [\%]} & {Maximum [\%]} \\
                              \cmidrule(r){1-1} \cmidrule(rl){2-3} \cmidrule(l){4-5}
      Diffusion & 0.40 & 2.63 & 2.01 & 17.44 \\
      Hybrid & 0.40 & 1.32 & 0.43 & 3.08 \\
      \bottomrule
    \end{tabular}
    \label{table:quarter-core-power}
  \end{table}
  \vspace{.2cm}

@@

\begin{frame}
  \frametitle{2-D MSRE Neutronics Simulation Results}
  \textbf{2-D Full-Core Normalized Channel Fission Rate Distribution}
  \begin{table}[htb]
    \footnotesize
    \centering
    \caption{Absolute mean and maximum percentage errors in the normalized channel fission rates of
    the 2-D \gls{MSRE} full-core models relative to OpenMC. The mean relative standard deviation of
    OpenMC normalized channel fission rates is 0.27\%.}
    \setlength\tabcolsep{1pt}
    \begin{tabular}{l S S S S S S S S}
      \toprule
      \multirow{2}{*}{Method} & \multicolumn{2}{c}{No Rod} & \multicolumn{2}{c}{Rod 1} & \multicolumn{2}{c}{Rod 1 \& 2} & \multicolumn{2}{c}{Rod 1, 2 \& 3} \\
                              & {Mean [\%]} & {Maximum [\%]} & {Mean [\%]} & {Maximum [\%]} & {Mean [\%]} & {Maximum [\%]} & {Mean [\%]} & {Maximum [\%]} \\
                              \cmidrule(r){1-1} \cmidrule(rl){2-3} \cmidrule(rl){4-5} \cmidrule(rl){6-7} \cmidrule(l){8-9}
      Diffusion & 0.45 & 2.95 & 0.94 & 12.61 & 1.35 & 15.34 & 1.67 & 17.09 \\
      Hybrid & 0.43 & 1.45 & 0.43 & 1.82 & 0.43 & 2.26 & 0.43 & 2.52 \\
      \bottomrule
    \end{tabular}
    \label{table:full-core-power}
  \end{table}
  \vspace{.2cm}

  \begin{itemize}
    \item Mean percentage error for the hybrid method remains consistent at 0.43\%.
    \item Significant improvement in maximum percentage error of the channel fission rate.
  \end{itemize}
\end{frame}

### 2024-12-12 presentation/3d-transient.tex
presentation edits
slide edits

\begin{frame}
  \frametitle{MSRE Rod Drop Experiment}
  \textbf{Rod Height}
  \begin{figure}[htb!]
    \centering
    \includegraphics[width=0.7\columnwidth]{rod-height}
    \caption{Evolution of rod height evaluated at each timestep within the first second of the rod
    drop simulation. The rod reaches its fully inserted height at $t=0.4046$ s.}
    \label{fig:rod-height}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{MSRE Rod Drop Experiment}
  \textbf{Nested Coupling Iteration Structure for the Rod Drop Simulation}
  \begin{figure}[t]
    \tikzstyle{every node}=[font=\small]
    \centering
    \includegraphics[width=\columnwidth]{images/nest-1}
    \caption{The nested iteration structure coupling the $S_N$, neutron diffusion, and \gls{DNP}
    solvers for the rod drop simulation using the hybrid $S_N$-diffusion method.}
    \label{fig:rod-drop-coupling}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{MSRE Rod Drop Experiment}
  \textbf{Neutron Count Rate Following Rod Drop}
  \begin{columns}
    \column{5.5cm}
    \begin{figure}[t]
      \centering
      \includegraphics[width=\columnwidth]{count-rate}
      \caption{Neutron count rate during the rod drop experiment from Moltres rod drop simulation.}
      \label{fig:count-rate}
    \end{figure}
    \column{5.5cm}
    \begin{itemize}
      \item Steep initial decline in neutron count rate as the rod drops
      \item Decline in neutron count rate slows at $t=0.5$ s due to presence of DNPs
      \item Convergence issues prevented the simulation from converging from $t = 0.8$ s
      \item I raised the convergence tolerance to help the simulation continue
    \end{itemize}
  \end{columns}
%  \begin{itemize}
%    \item Moltres underpredicted the integral neutron count rate by approximately 20 \%.
%    \item Potential sources of error
%    \begin{itemize}
%      \item Uncertainty in the initial neutron count rate
%      \item Miscalculation of -1500 pcm reactivity withdrawal
%    \end{itemize}
%  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{MSRE Rod Drop Experiment}
  \textbf{Integral Neutron Count Following Rod Drop}
  \begin{columns}
    \column{5.5cm}
    \begin{figure}[t]
      \centering
      \includegraphics[width=\columnwidth]{integral-count}
      \caption{Integral neutron count during the rod drop experiment from \gls{MSRE} experimental data
      and hybrid method numerical results.}
      \label{fig:integral-count}
    \end{figure}
    \column{5.5cm}
    \begin{itemize}
      \item Moltres reproduces the expected trend in the integral neutron count rate
      \item Slight underprediction relative to MSRE rod drop experimental data
      \item Underprediction may be due to experimental uncertainty in $^{235}$U concentration,
        initial \& final rod height, initial neutron count rate.
    \end{itemize}
  \end{columns}
%  \begin{itemize}
%    \item Moltres underpredicted the integral neutron count rate by approximately 20 \%.
%    \item Potential sources of error
%    \begin{itemize}
%      \item Uncertainty in the initial neutron count rate
%      \item Miscalculation of -1500 pcm reactivity withdrawal
%    \end{itemize}
%  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{3-D Modeling with the Hybrid Method}
  \begin{block}{\textbf{Difficulties Faced During 3-D Modeling}}
  \begin{itemize}
    \item Poor convergence rate relative to 1-D \& 2-D modeling
    \begin{itemize}
      \item Likely due to increased streaming effects in 3-D near-void (air) regions in the reactor
    \end{itemize}
    \item Significant memory requirements
    \item Lagged control rod positions in fixed point iterations affecting convergence in time-dependent
      simulations $\Rightarrow$ simulation requires smaller timestep sizes
  \end{itemize}
\end{block}
\end{frame}

>>>>

\begin{frame}
  \frametitle{MSRE Rod Drop Modeling Approach}
  \textbf{Nested Coupling Iteration Structure for the Rod Drop Simulation}
  \begin{figure}[t]
    \tikzstyle{every node}=[font=\small]
    \centering
    \includegraphics[width=\columnwidth]{images/nest-1}
    \caption{The nested iteration structure coupling the $S_N$, neutron diffusion, and \gls{DNP}
    solvers for the rod drop simulation using the hybrid $S_N$-diffusion method.}
    \label{fig:rod-drop-coupling}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{MSRE Rod Drop Simulation Results}
  \textbf{Neutron Count Rate Following Rod Drop}
  \begin{columns}
    \column{5.5cm}
    \begin{figure}[t]
      \centering
      \includegraphics[width=\columnwidth]{count-rate}
      \caption{Neutron count rate during the rod drop experiment from Moltres rod drop simulation.}
      \label{fig:count-rate}
    \end{figure}
    \column{5.5cm}
    \begin{itemize}
      \item Steep initial decline in neutron count rate as the rod drops
      \item Decline in neutron count rate slows at $t=0.5$ s due to presence of DNPs
      \item Convergence issues prevented the simulation from converging from $t = 0.8$ s
      \item Raised the convergence tolerance value after $t=0.8$ s to help the simulation continue
    \end{itemize}
  \end{columns}
%  \begin{itemize}
%    \item Moltres underpredicted the integral neutron count rate by approximately 20 \%.
%    \item Potential sources of error
%    \begin{itemize}
%      \item Uncertainty in the initial neutron count rate
%      \item Miscalculation of -1500 pcm reactivity withdrawal
%    \end{itemize}
%  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{MSRE Rod Drop Simulation Results}
  \textbf{Integral Neutron Count Following Rod Drop}
  \begin{columns}
    \column{5.5cm}
    \begin{figure}[t]
      \centering
      \includegraphics[width=\columnwidth]{integral-count}
      \caption{Integral neutron count during the rod drop experiment from \gls{MSRE} experimental data
      and hybrid method numerical results.}
      \label{fig:integral-count}
    \end{figure}
    \column{5.5cm}
    \begin{itemize}
      \item Moltres reproduces the expected trend in the integral neutron count rate.
      \item Slight underprediction relative to MSRE rod drop experimental data
      \item Underprediction may be due to experimental uncertainty in $^{235}$U concentration,
        initial \& final rod height, initial neutron count rate.
    \end{itemize}
  \end{columns}
%  \begin{itemize}
%    \item Moltres underpredicted the integral neutron count rate by approximately 20 \%.
%    \item Potential sources of error
%    \begin{itemize}
%      \item Uncertainty in the initial neutron count rate
%      \item Miscalculation of -1500 pcm reactivity withdrawal
%    \end{itemize}
%  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{3-D Modeling with the Hybrid Method}
  \begin{block}{\textbf{Difficulties Faced During 3-D Modeling}}
  \begin{itemize}
    \item Slow convergence rate relative to 1-D \& 2-D modeling
    \begin{itemize}
      \item Likely due to increased streaming effects in 3-D near-void (air) regions in the reactor
    \end{itemize}
    \item Significant memory requirements
    \item Lagged control rod positions in fixed point iterations affecting convergence in time-dependent
      simulations $\Rightarrow$ simulation requires smaller timestep sizes
  \end{itemize}
\end{block}
\end{frame}

### 2024-12-12 presentation/3d.tex
slide edits

\begin{frame}
  \frametitle{3-D MSRE Neutronics Simulation Results}
  \textbf{MSRE Rod Worth Measurements}
  \begin{table}[t]
    \centering
    \caption{Total rod worth of Rod 1 when fully inserted.}
    \small
    \begin{tabular}{l S[table-format=4(2)] S}
      \toprule
       & {$\rho_\text{worth}$ [pcm]} & {Percentage discrepancy [\%]}\\
       \cmidrule(rl){2-2} \cmidrule(l){3-3}
      \gls{MSRE} experimental data & 2250(67) & {-}\\
      OpenMC (This work) & 2364(44) & 5.1 \\
      Hybrid (This work) & 2345 & 4.2 \\
      Diffusion (This work) & 2725 & 21.1 \\
      \bottomrule
    \end{tabular}
    \label{table:rod-worth}
  \end{table}
  \vspace{.2cm}

@@

\begin{frame}
  \frametitle{3-D MSRE Neutronics Simulation Results}
  \textbf{Computational Performance}
  \begin{itemize}
    \item All simulations ran on the Polaris supercomputer system at Argonne National Laboratory.
    \item Each 3-D full-core simulation consisted of 750M and 1.69B degrees of freedom for the
      neutron diffusion and $S_N$ subsolvers, respectively.
    \item 3-D full-core simulations required at least 40 compute nodes with 512 GB RAM each due to
      strict memory requirements (significant improvements in memory use is possible) and took 2.2
      h to complete.
    \item The hybrid method took about four times longer than the neutron diffusion method.
    \item 30 \% of compute time spent on data transfers between the neutron diffusion and $S_N$
      subsolvers (Reduced to 18 \% in subsequent simulations after optimizations)
  \end{itemize}
\end{frame}

>>>>

\begin{frame}
  \frametitle{3-D MSRE Neutronics Simulation Results}
  \textbf{MSRE Rod Worth Measurements}
  \begin{table}[t]
    \centering
    \caption{Total rod worth of Rod 1 when fully inserted.}
    \small
    \begin{tabular}{l S[table-format=4(2)] S}
      \toprule
       & {$\rho_\text{worth}$ [pcm]} & {Percentage discrepancy [\%]}\\
       \cmidrule(rl){2-2} \cmidrule(l){3-3}
      \gls{MSRE} experimental data & 2250(67) & {-}\\
      OpenMC (This work) & 2364(44) & 5.1 \\
      Hybrid (This work) & 2345 & 4.2 \\
      Diffusion (This work) & 2725 & 21.1 \\
      \bottomrule
    \end{tabular}
    \label{table:rod-worth}
  \end{table}
  \vspace{.1cm}

@@

\begin{frame}
  \frametitle{3-D MSRE Neutronics Simulation Results}
  \textbf{Computational Performance}
  \begin{itemize}
    \item All simulations ran on the Polaris supercomputer system at Argonne National Laboratory.
    \item Each 3-D full-core simulation consisted of 750M and 1.69B degrees of freedom for the
      neutron diffusion and $S_N$ subsolvers, respectively.
    \item 3-D full-core simulations required at least 40 compute nodes with 512 GB RAM each due to
      strict memory requirements (significant improvements in memory use is possible) and took 2.2
      h to complete.
    \item The hybrid method took about four times longer than the neutron diffusion method.
    \item 30\% of compute time spent on data transfers between the neutron diffusion and $S_N$
      subsolvers (reduced to 18\% in subsequent simulations after optimizations).
  \end{itemize}
\end{frame}
